\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation \dg{for Machine Learning}

### 2018-05-06 ccs/ld.tex
reviews incorporate

In this section we prove correctness and security of our \tool compiler.
\dg{Put a warning that this section is technical and not prerequisite for understanding later section.}
%We formalize our source, intermediate and circuit languages. 
%An example of a program in our source language is provided in \figureref{ex-sml}.
%Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
We first formalize our source language (an example program being
\figureref{ex-sml}), and its runtime semantics.
This semantics describes the ``trusted third party"
execution semantics of the source programs and
generates observations corresponding to the values revealed to the
parties.
%
We then present the compilation rules that type check a program in the
source language and generate a program in the intermediate
language (an example program being \figureref{ex-aby}).
%
Next, we present the runtime semantics of our intermediate language
that evaluates to a circuit by ``evaluating away'' the public parts
and the arrays. Crucially, this step does not have access to the secret
inputs; those are processed by our distributed circuit semantics that
model the \mpc back-end.
%
Evaluation in this distributed setting involves the parties running an
interactive protocol. This step, like  the source semantics, emits
observations corresponding to the values revealed to the parties.
%Finally, we formalize the distributed circuit semantics (of the cryptographic back-end) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observationscorresponding to the values revealed to the parties.

@@

\begin{figure}[H]
  \footnotesize
  \fbox{$\Gamma \vdash e : \tau \leadsto \widetilde{e}$}\quad\quad
  \fbox{$\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$}  \[
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-UInt}}]
               {
               }
               {
                 \Gamma \vdash n : \kw{uint}^{\mathcal{P}} \leadsto n
               }
               \hspace{0.1cm}
     \inferrule*[lab={\footnotesize{T-Bool}}]
               {
                 c = \top \vee c = \bot
               }
               {
                 \Gamma \vdash c : \kw{bool}^{\mathcal{P}} \leadsto c 
               }

@@

\paragraph{Correctness Theorem.} We prove that all well typed programs always terminate (array indices are always in bounds, there are no unbounded loops, etc.) and the \mpc protocol produces the same outputs as the source program. That is, if a source statement $s$ is well-typed, and compiles to $\widetilde{s}$ in the intermediate language, then $s$ terminates in the source semantics with observations $O$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the circuit semantics with the same observations $O$. Formally, the the correctness theorem is as follows (the environments on the left of $\vdash$ are empty and we elide the environments on the right of $\vdash$ for brevity):

%\subsubsection*{Correctness theorem}
\old{
Finally, the correctness theorem is as follows (the environments on
the left of $\vdash$ are empty and we elide the environments on the
right of $\vdash$ for brevity):}

@@

\old{The theorem states that if a source statement $s$ is well-typed, and
compiles to $\widetilde{s}$ in the intermediate language, then $s$ terminates in the source
semantics with observations $O$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
circuit semantics with the same observations $O$. 
Therefore, well typed programs always terminate (array indices are always in bounds, there are no unbounded loops, etc.) and the \mpc protocol produces the same outputs as the source program.}

\dg{We prove the theorem in Appendix~\ref{}.}
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.

>>>>

In this section we prove correctness and security of our \tool compiler.
The readers who are interested in using the compiler as a black box can
move directly to  Section~\ref{sec:pipe}.
%\dg{Put a warning that this section is technical and not prerequisite for understanding later section.}
%We formalize our source, intermediate and circuit languages. 
%An example of a program in our source language is provided in \figureref{ex-sml}.
%Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
We first formalize our source language (an example program being
\figureref{ex-sml}), and its runtime semantics.
This semantics describes the ``trusted third party"
execution semantics of the source programs and
generates observations corresponding to the values revealed to the
parties.
%
We then present the compilation rules that type check a program in the
source language and generate a program in the intermediate
language (an example program being \figureref{ex-aby}).
%
Next, we present the runtime semantics of our intermediate language
that evaluates to a circuit by ``evaluating away'' the public parts
and the arrays. Crucially, this step does not have access to the secret
inputs; those are processed by our distributed circuit semantics that
model the \mpc back-end.
%
Evaluation in this distributed setting involves the parties running an
interactive protocol. This step, like  the source semantics, emits
observations corresponding to the values revealed to the parties.
%Finally, we formalize the distributed circuit semantics (of the cryptographic back-end) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observationscorresponding to the values revealed to the parties.

@@

\begin{figure}[t]
  \footnotesize
  \fbox{$\Gamma \vdash e : \tau \leadsto \widetilde{e}$}\quad\quad
  \fbox{$\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$}  \[
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-UInt}}]
               {
               }
               {
                 \Gamma \vdash n : \kw{uint}^{\mathcal{P}} \leadsto n
               }
               \hspace{0.1cm}
     \inferrule*[lab={\footnotesize{T-Bool}}]
               {
                 c = \top \vee c = \bot
               }
               {
                 \Gamma \vdash c : \kw{bool}^{\mathcal{P}} \leadsto c 
               }

@@

\paragraph{Correctness Theorem.} We prove that all well typed programs always terminate successfully (array indices are always in bounds, there are no unbounded loops, etc.) and the \mpc protocol produces the same outputs as the source program. That is, if a source statement $s$ is well-typed, and compiles to $\widetilde{s}$ in the intermediate language, then $s$ terminates in the source semantics with observations $O$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the circuit semantics with the same observations $O$. Formally, the correctness theorem is as follows (the environments on the left of $\vdash$ are empty and we elide the environments on the right of $\vdash$ for brevity):

%\subsubsection*{Correctness theorem}

%Finally, the correctness theorem is as follows (the environments onthe left of $\vdash$ are empty and we elide the environments on the right of $\vdash$ for brevity):

@@

%%\old{The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in the intermediate language, then $s$ terminates in the source
%semantics with observations $O$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with the same observations $O$. 
%Therefore, well typed programs always terminate (array indices are always in bounds, there are no unbounded loops, etc.) and the \mpc protocol produces the same outputs as the source program.}

We prove the theorem in Appendix~\ref{app:formal}.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.

### 2018-05-06 ccs/pipe.tex
minor
reviews incorporate

\newcommand{\prog}{s}
\newcommand{\progn}{t}
\newcommand{\seq}{||}
\newcommand{\stateq}{q}

We  now describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
\dg{Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}. \dg{We describe it only in the arithmetic setting but the same can be done in the Boolean setting as well.}

@@

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\stateq_0
= \bot$. Without
loss of generality, let all $\stateq_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\stateq_0$), and runs $\prog_1$ (as defined above) to
compute $\stateq_1$ and then outputs $o_1 = \stateq_1 + r_1$ {\em only
  to} Bob\footnote{While the description of the scheme here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
  }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\stateq_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\stateq_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\stateq_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties.

@@

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, we first decompose the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
\dg{Automating the  decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program.
Resource analysis of programs is a well-known hard problem~\cite{raml}
 and we describe a heuristic analysis in Appendix~\ref{app:pipe-idea}.}
% \nc{I changed the heading.}

>>>>

\newcommand{\prog}{s}
\newcommand{\progn}{t}
\newcommand{\mprog}{u}
\newcommand{\seq}{||}
\newcommand{\stateq}{q}

We  now describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

@@

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\stateq_0
= \bot$. Without
loss of generality, let all $\stateq_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\stateq_0$), and runs $\prog_1$ (as defined above) to
compute $\stateq_1$ and then outputs $o_1 = \stateq_1 + r_1$ {\em only
  to} Bob\footnote{While the description of the scheme here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
 }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\stateq_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\stateq_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\stateq_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties. Although we have used arithmetic sharing here, Boolean sharing can be used to achieve the same effect.

@@

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, we first decompose the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the  decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program.
Resource analysis of high-level programs is a well-known hard problem~\cite{raml}
and we describe a heuristic analysis.

To build $s_1$, we consider the longest
prefix of $s$ whose computation {\it size} is below the threshold enforced by the available memory of the machine.
If $\prog = \prog_1; \prog_r$ then we recurse on $\prog_r$ to obtain $\prog_2,\ldots,\prog_k$.
For a program $\mprog$, to estimate ${\it size}(\mprog)$, we need to discuss three important cases: if $\mprog\equiv\mprog_1;\mprog_2$
then ${\it size}(\mprog)={\it size}(\mprog_1)+{\it size}(\mprog_2)$; if $\mprog\equiv\ite{e_1}{\mprog_1}{\mprog_2}$ then ${\it size}(\mprog)=\max({\it size}(\mprog_1),{\it size}(\mprog_2))$; if $s\equiv\forl{i}{n_1}{n_2}{\mprog_1}$ then
${\it size}(\mprog)=(n_2-n_1){\it size}(\mprog_1)$. If $(n_2-n_1){\it size}(\mprog_1)$ is above the threshold then
we replace $\mprog$ by 
\[\forl{i}{n_1}{\frac{n_1+n_2}{2}}{\mprog_1}; \forl{i}{\frac{n_1+n_2}{2}}{n_2}{\mprog_1}\]
 and recurse to find the prefix again.
This heuristic analysis is sufficient for the benchmarks discussed in our evaluation.

% \nc{I changed the heading.}

### 2018-05-06 ccs/related.tex
reviews incorporate

\mpc backends  have made  tremendous progress in the last decade.
For example, the circuits can be optimized for depth~\cite{ddkssz15,cbmcgcdepth}, large garbled circuits can be pipelined~\cite{yao-pipe}, and oblivious RAM~\cite{oram1,oram2} can be used to hide access patterns of MIPS code~\cite{mips}. Incorporating these backends would only improve the performance and scalability of \tool implementations.

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

>>>>

\mpc backends  have made  tremendous progress in the last decade.
For example, the circuits can be optimized for depth~\cite{ddkssz15,cbmcgcdepth}, large garbled circuits can be pipelined~\cite{yao-pipe,oblivm}, online complexity can be reduced at the cost of offline complexity~\cite{groce}, encrypted values output from a garbled circuit can be reused~\cite{ReuseOrLose} and oblivious RAM~\cite{oram1,oram2} can be used to hide access patterns of MIPS code~\cite{mips}. 
Incorporating these backends would only improve the performance and scalability of \tool implementations.

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.

% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

### 2018-05-06 ccs/security.tex
reviews incorporate

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.

>>>>

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}\dg{ and provides provable security against all side-channel attacks}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.
